---
title: "Assignment 01"
author: "Martina Mileva"
date: "`r Sys.Date()`"
output: html_document
---

<https://github.com/martinamileva/BIOL432_Assignment1>

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

source("http://bit.ly/theme_pub")
theme_set(theme_pub())
```

```{r}
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```

## Running the scripts to create the measurement data:

**dataGenerato.R**

Creates 4 vectors (Species, Limb_width, Limb_length, and Observer) and combines them into a data frame.

```{r}
source('dataGenerato.R')
```

**volumeEstimato.R**

Adds column to the data frame that estimates volume from Limb_width and Limb_length, using the formula:

$V =\pi l (\frac{w}{2}) ^2$

```{r}
source('volumeEstimato.R')
```

1.  Loading the revised measurements.csv:

```{r}
measurements <- read.csv("measurements.csv")
```

2.  Using dplyr to sort the data by species, then by observer, then by limb volume:

```{r}
measurements <- measurements %>%
  group_by(Species, Observer, Volume)
```

3.  Creating a table that shows average volume for each species:

```{r}
Mean_Vol <- measurements %>%
  group_by(Species) %>%
  summarize(Mean_Vol=mean(Volume))
```

4.  Creating a table that shows number of observations for each combination of species and observer:

```{r}
Num_Obv <- measurements %>% group_by(Species, Observer) %>%
  summarize(Num_Obv=n())
```

5.  Creating a box plot to compare key features of volume distributions for each species:

```{r}
ggplot(measurements, aes(y=Volume, x=Species, group=Species, fill=Species)) + geom_boxplot() + labs(x="Species", y=bquote('Limb volume'~(mm^2)))
```
**Fig. 1.** Limb volume in mm^2^ for 5 different bat species. 


6.  Creating a multi-panel plot to show frequency histograms for each species.

```{r}
Freq <- measurements %>%
  select(Species, Volume)

ggplot(Freq, aes(x=Volume, fill=Species)) + geom_histogram() + facet_grid(vars(Species)) + labs(y="Frequency", x=bquote('Limb volume'~(mm^2)))
```
**Fig. 2.** Frequency distribution for limb volume in mm^2^ for 5 different bat species. 

